Prepare Data

### 2024-07-16 src/analysis/Analysis.Rmd
update data

# Analyses
```{r "data for analyses"}
load(here("data/intermediate/cleaned_data_nl.RData"))
load(here("data/intermediate/cleaned_data_us.RData"))
```

@@

```{r "balance-checks", fig.height=12, fig.width=8}
source(here("src/analysis/balance-test.R"))
df
```

## Baseline Model
```{r "baseline", fig.align="center", fig.height=4, fig.width=8}
source(here("src/analysis/baseline.R"))
b
rm(b_b, b1, b2, d, df, df_nl, df_us, tmp)
```

```{r "issues", fig.align="center", fig.height=16, fig.width=8}
source(here("src/analysis/issue_specific.R"))
b_i
rm(b1, b2, d, df, df_nl, df_us, tmp)
```

## Ideological Bias hypothesis
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1a
p1b
rm(df, df_nl, df_us, h1a, h1b, tmp)
```

## Overinterpretation Hypotheses
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2a
p2b
p2c1
p2c2
rm(df, df_nl, df_us, h2a, h2a_2, h2b, h2b_2, tmp, tmpp)
```

## Masking Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3a
p3b
p3c1
p3c2
rm(df, df_nl, df_us, h3a, h3a_2, h3b, h3b_2,h3b_bs, h3b_2bs, tmp, tmpp)
```

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_b1
p_b2
p_e1a
p_e1b

source(here("src/analysis/profile_resp.R"))
kbl(e1_nlp, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

>>>>

# Analyses
```{r "data for analyses"}
load(here("data/intermediate/cleaned_data_joined.RData"))
```

@@

```{r "balance-checks", fig.height=12, fig.width=8}
#source(here("src/analysis/balance-test.R"))
#df
```

## Baseline Model
```{r "baseline", fig.align="center", fig.height=4, fig.width=8}
source(here("src/analysis/baseline.R"))
b
rm(b_b, b1, b2, df, df_nl, df_us, tmp)
```

```{r "issues", fig.align="center", fig.height=16, fig.width=8}
source(here("src/analysis/issue_specific.R"))
b_i
rm(b1, b2, df, df_nl, df_us, tmp, issues_nl, issues_us, i)
```

## Ideological Bias hypothesis
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1a
p1b

(p1b_1+p1b_2)/(p1b_3 + p1b_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
rm(df, df_nl, df_us, h1a, h1b, p1b_1, 
   pred1b_1, pred1b_2, pred1b_3, pred1b_4, tmp)
```

## Overinterpretation Hypotheses
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2a
p2b
p2c1
p2c2

(p2a_1+p2a_2)/(p2a_3 + p2a_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

(p2b_1+p2b_2)/(p2b_3 + p2b_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
rm(df, df_nl, df_us, h2a, h2a_2, h2b, h2b_2, tmp, tmpp,
   pred2a_1, pred2a_2, pred2a_3, pred2a_4, 
   pred2b_1, pred2b_2, pred2b_3, pred2b_4)
```

## Masking Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3a
p3b
p3c1
p3c2

(p3a_1+p3a_2)/(p3a_3 + p3a_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

(p3b_1+p3b_2)/(p3b_3 + p3b_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
rm(df, df_nl, df_us, h3a, h3a_2, h3b, 
   h3b_2,h3b_bs, h3b_2bs, tmp, tmpp,
   pred3a_1, pred3a_2, pred3a_3, pred3a_4, 
   pred3b_1, pred3b_2, pred3b_3, pred3b_4)
```

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_b1
p_b2
p_e1a
p_e1b
```

```{r "explor2", eval=FALSE}
source(here("src/analysis/profile_resp.R"))
kbl(e1_nlp, booktabs =T, caption = "\\label{tab:conditions}Profile Dutch Stance Annotators") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "7cm") %>%
  column_spec(2, width = "7cm")

### 2024-07-16 src/data-processing/prepare-data.Rmd
update data

```{r "get & clean data", results="hide"}
#Clean Dutch Data
d_nl <- read_sav(here("data/raw-private/NLOZ2206_Mariken_Bias-experiment.sav"))
source(here("src/data-processing/clean_data_nl.R"))

#Clean US Data
d_us <- fetch_survey(surveyID = "SV_86XBcsFUJka9eke", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
source(here("src/data-processing/clean_data_us.R"))
```

## Save Data for Analysis
```{r "save data"}
save(d_nl, file = here("data/intermediate/cleaned_data_nl.RData"))
save(d_us, file = here("data/intermediate/cleaned_data_us.RData"))
```

@@

### Dependent Variable by Issue
```{r "Dependent Variable", echo=F, fig.width=15, fig.height=8}
p1 <- d_nl %>%
  group_by(stance,issue,specification, masking) %>% 
  count() %>% 
  mutate(stance = ifelse(stance==0, "Not Correctly identified stance",
                         "Correctly identified stance"),
         specification = ifelse(specification == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == "Masked", "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue, x = n, fill = stance)) +
  geom_col() +
  facet_grid(masking~specification) +
  labs(x = "", y = "", 
       title = "Dutch Data") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

p2 <- d_us %>%
  group_by(stance,issue,specification, masking) %>% 
  count() %>% 
  mutate(stance = ifelse(stance==0, "Not Correctly identified stance",
                         "Correctly identified stance"),
         specification = ifelse(specification == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == "Masked", "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue, x = n, fill = stance)) +
  geom_col() +
  facet_grid(masking~specification) +
  labs(x = "", y = "", 
       title = "US Data") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

p1 + p2 + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

```

### Covariates
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
rm(p1,p2)
p <- d_nl %>% select(distance, PT7, PT6) %>% 
  pivot_longer(cols = everything(),
               values_to = "score") %>% 
  group_by(name) %>% 
  summarise(m = mean(score),
            stdev = sd(score)) %>% 
  mutate(name = recode(name,
                       `distance` = "Ideological Distance \n(> = More Distance)",
                       `PT6` = "Ideological Self Placement \n(0 = Left, 10 = Right)",
                       `PT7` = "Political Knowledge \n(0 = Low, 6 = High)"),
         country = "The Netherlands")

p2 <- d_us %>% 
  select(distance, PT7, PT7b, PT6) %>% 
  pivot_longer(cols = everything(),
               values_to = "score") %>% 
  group_by(name) %>% 
  summarise(m = mean(score),
            stdev = sd(score)) %>% 
  mutate(name = recode(name,
                       `distance` = "Ideological Distance \n(> = More Distance)",
                       `PT6` = "Ideological Self Placement \n(0 = Extremely Liberal, 6 = Extremely Conservative)",
                       `PT7` = "Political Knowledge \n(0 = Low, 3 = High)",
                       `PT7b` = "Bullshit Receptivity \n(0 = Low, 5 = High)"),
         country = "United States")

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=F, warning=F, fig.width=15, fig.height=15}
d_nl %>%
  drop_na() %>% 
  select(`Age` = D1,
         `Gender` = D2,
         `Education` = D3,
         `Region`  = D4,
         `Income`  = D5,
         `Job`  = D6,
         `Vote Recall`  = PT1,
         `Position: Immigration`  = PT2,
         `Position: Climate`  = PT3,
         `Position: Tax`  = PT4,
         `Position: EU`  = PT5,
         `Ideology`  = PT6,
         `Political Knowledge` = PT7,
         `Distance to Political Party` = distance,
         `Stance` = stance) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study",
  subtitle = "Dutch Data"
)

d_us %>%
  drop_na() %>% 
  select(`Age` = D1,
         `Gender` = D2,
         `Education` = D3,
         `Region`  = D4,
         `Income`  = D5,
         `Job`  = D6,
         `PID`  = PT1,
         `PID Strength` = PT1b,
         `Position: Immigration`  = PT2,
         `Position: Climate`  = PT3,
         `Position: Tax`  = PT4,
         `Position: EU`  = PT5,
         `Ideology`  = PT6,
         `Political Knowledge` = PT7,
         `Bullshit Receptivity` = PT7b,
         `Distance to Political Party` = distance,
         `Stance` = stance) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study",
  subtitle = "US Data"
)
```

>>>>

```{r "get & clean data", results="hide"}
#Load Dutch Data
d_nl <- read_sav(here("data/raw-private/NLOZ2206_Mariken_Bias-experiment.sav"))

#Load US Data
d_us <- fetch_survey(surveyID = "SV_86XBcsFUJka9eke", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
#Clean data
source(here("src/data-processing/clean_data.R"))
```

## Save Data for Analysis
```{r "save data"}
save(d, file = here("data/intermediate/cleaned_data_joined.RData"))
```

@@

### Dependent Variable by Issue
```{r "Dependent Variable", echo=F, fig.width=15, fig.height=10}
p1a <- d |> 
  filter(country == "NL") |> 
  mutate(issue2 = recode(issue,
                         `tax on carbon emissions` = "Climate",
                         `a wealth tax for the richest Americans` = "Tax",
                         `the tax system` = "Tax",
                         `military presence in the Pacific Ocean` = "EU/Foreign Policy",
                         `military build-up in the Pacific Ocean` = "EU/Foreign Policy",
                         `immigranten` = "Immigration",
                         `immigratie` = "Immigration",
                         `het tegengaan van stikstofuitstoot` = "Climate",
                         `het stikstofbeleid` = "Climate",
                         `het verhogen van het belastingstarief voor de hoogste inkomens` = "Tax",
                         `het belastingstelsel` = "Tax",
                         `de  rol van Nederland in de Europese Unie` = "EU/Foreign Policy",
                         `het lidmaatschap van de Europese Unie voor Nederland` = "EU/Foreign Policy")) |> 
  group_by(stance_nlp,issue2,specified, masking, country) %>% 
  count() %>% 
  drop_na(stance_nlp) |> 
  mutate(stance_nlp = recode(stance_nlp,
                             `correct` = "Correct",
                             `incorrect` = "Incorrect"),
         specified = ifelse(specified == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == 1, "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue2, x = n, fill = stance_nlp)) +
  geom_col() +
  facet_grid(masking~specified) +
  labs(x = "", y = "",
       title = "NL Data - Strict Interpretation") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

p1b <- d |> 
  filter(country == "NL") |> 
  mutate(issue2 = recode(issue,
                         `tax on carbon emissions` = "Climate",
                         `a wealth tax for the richest Americans` = "Tax",
                         `the tax system` = "Tax",
                         `military presence in the Pacific Ocean` = "EU/Foreign Policy",
                         `military build-up in the Pacific Ocean` = "EU/Foreign Policy",
                         `immigranten` = "Immigration",
                         `immigratie` = "Immigration",
                         `het tegengaan van stikstofuitstoot` = "Climate",
                         `het stikstofbeleid` = "Climate",
                         `het verhogen van het belastingstarief voor de hoogste inkomens` = "Tax",
                         `het belastingstelsel` = "Tax",
                         `de  rol van Nederland in de Europese Unie` = "EU/Foreign Policy",
                         `het lidmaatschap van de Europese Unie voor Nederland` = "EU/Foreign Policy")) |> 
  group_by(stance_ss,issue2,specified, masking, country) %>% 
  count() %>% 
  drop_na(stance_ss) |> 
  mutate(stance_ss = recode(stance_ss,
                             `correct` = "Correct",
                             `incorrect` = "Incorrect"),
         specified = ifelse(specified == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == 1, "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue2, x = n, fill = stance_ss)) +
  geom_col() +
  facet_grid(masking~specified) +
  labs(x = "", y = "",
       title = "NL Data - Lenient Interpretation") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

p2a <- d |> 
  filter(country == "US") |> 
  mutate(issue2 = recode(issue,
                         `tax on carbon emissions` = "Climate",
                         `a wealth tax for the richest Americans` = "Tax",
                         `the tax system` = "Tax",
                         `military presence in the Pacific Ocean` = "EU/Foreign Policy",
                         `military build-up in the Pacific Ocean` = "EU/Foreign Policy",
                         `immigranten` = "Immigration",
                         `immigratie` = "Immigration",
                         `het tegengaan van stikstofuitstoot` = "Climate",
                         `het stikstofbeleid` = "Climate",
                         `het verhogen van het belastingstarief voor de hoogste inkomens` = "Tax",
                         `het belastingstelsel` = "Tax",
                         `de  rol van Nederland in de Europese Unie` = "EU/Foreign Policy",
                         `het lidmaatschap van de Europese Unie voor Nederland` = "EU/Foreign Policy")) |> 
  group_by(stance_nlp,issue2,specified, masking, country) %>% 
  count() %>% 
  drop_na(stance_nlp) |> 
  mutate(stance_nlp = recode(stance_nlp,
                             `correct` = "Correct",
                             `incorrect` = "Incorrect"),
         specified = ifelse(specified == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == 1, "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue2, x = n, fill = stance_nlp)) +
  geom_col() +
  facet_grid(masking~specified) +
  labs(x = "", y = "", 
       title = "US Data - Strict Interpretation") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

p2b <- d |> 
  filter(country == "US") |> 
  mutate(issue2 = recode(issue,
                         `tax on carbon emissions` = "Climate",
                         `a wealth tax for the richest Americans` = "Tax",
                         `the tax system` = "Tax",
                         `military presence in the Pacific Ocean` = "EU/Foreign Policy",
                         `military build-up in the Pacific Ocean` = "EU/Foreign Policy",
                         `immigranten` = "Immigration",
                         `immigratie` = "Immigration",
                         `het tegengaan van stikstofuitstoot` = "Climate",
                         `het stikstofbeleid` = "Climate",
                         `het verhogen van het belastingstarief voor de hoogste inkomens` = "Tax",
                         `het belastingstelsel` = "Tax",
                         `de  rol van Nederland in de Europese Unie` = "EU/Foreign Policy",
                         `het lidmaatschap van de Europese Unie voor Nederland` = "EU/Foreign Policy")) |> 
  group_by(stance_ss,issue2,specified, masking, country) %>% 
  count() %>% 
  drop_na(stance_ss) |> 
  mutate(stance_ss = recode(stance_ss,
                             `correct` = "Correct",
                             `incorrect` = "Incorrect"),
         specified = ifelse(specified == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == 1, "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue2, x = n, fill = stance_ss)) +
  geom_col() +
  facet_grid(masking~specified) +
  labs(x = "", y = "", 
       title = "US Data - Lenient Interpretation") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

(p2a + p2b)/ (p1a + p1b) +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

### Covariates
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=6, fig.height=6}
rm(p1a, p1b, p2a, p2b)
p <- d %>% 
  filter(country=="NL") |> 
  select(distance, PT7, PT6) %>% 
  pivot_longer(cols = everything(),
               values_to = "score") %>% 
  group_by(name) %>% 
  summarise(m = mean(score),
            stdev = sd(score)) %>% 
  mutate(name = recode(name,
                       `distance` = "Ideological Distance \n(> = More Distance)",
                       `PT6` = "Ideological Self Placement \n(0 = Left/Liberal, 1 = Right/Conservative)",
                       `PT7` = "Political Knowledge \n(0 = Low, 1 = High)"),
         country = "The Netherlands")

p2 <-d %>% 
  filter(country=="US") |> 
  select(distance, PT7, PT7b, PT6) %>% 
  mutate(PT7b = PT7b / 5) |> 
  pivot_longer(cols = everything(),
               values_to = "score") %>% 
  drop_na(score) |> 
  group_by(name) %>% 
  summarise(m = mean(score),
            stdev = sd(score)) %>% 
  mutate(name = recode(name,
                       `distance` = "Ideological Distance \n(> = More Distance)",
                       `PT6` = "Ideological Self Placement \n(0 = Left/Liberal, 1 = Right/Conservative)",
                       `PT7` = "Political Knowledge \n(0 = Low, 1 = High)",
                       `PT7b` = "Bullshit Receptivity \n(0 = Low, 1 = High)"),
         country = "United States")

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=F, warning=F, fig.width=8, fig.height=8}
d %>%
  filter(country == "NL") |> 
  select(`Age` = D1,
         `Gender` = D2,
         `Education` = D3,
         `Region`  = D4,
         `Income`  = D5,
         `Job`  = D6,
         `Vote Recall`  = PT1,
         `Position: Immigration`  = PT2,
         `Position: Climate`  = PT3,
         `Position: Tax`  = PT4,
         `Position: EU`  = PT5,
         `Ideology`  = PT6,
         `Political Knowledge` = PT7,
         `Distance to Political Party` = distance,
         `Stance` = stance) %>%
  drop_na() %>% 
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study",
  subtitle = "Dutch Data"
)

d %>%
  filter(country == "US") |> 
  select(`Age` = D1,
         `Gender` = D2,
         `Education` = D3,
         `Region`  = D4,
         `Income`  = D5,
         `Job`  = D6,
         `PID`  = PT1,
         #`PID Strength` = PT1b,
         `Position: Immigration`  = PT2,
         `Position: Climate`  = PT3,
         `Position: Tax`  = PT4,
         `Position: Foreign Policy`  = PT5,
         `Ideology`  = PT6,
         `Political Knowledge` = PT7,
         `Bullshit Receptivity` = PT7b,
         `Distance to Political Party` = distance,
         `Stance` = stance) %>%
    drop_na() %>% 
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study",
  subtitle = "US Data"
)
```
